\subsection{{Interpretable Machine Learning for Flare Prediction | \textit{Python, Tensorflow, ML, DL, XAI} \hfill Oct 2023 - Ongoing}}
{\textit{Research Assistant} \hfill \href{https://github.com/vinay-ram1999/SolarFlareNet}{Project Source}}
\begin{zitemize}
\item {Integrated XAI tools like LIME, SHAP, PDP and ALE plots into multiple machine learning and deep learning tools used for predictiong space weather.}
\item {Pioneered the integration of interpretability techniques into transformer-based machine learning model named ``SolarFlareNet''.}
\item {Studied the feature importance and feature interactions between the SHARP magnetic parameters used to forecast solar flares for NOAA selected active regions.}
\end{zitemize}


\subsection{{eComputer Store Database System | \textit{MySQL, Python, Streamlit, Pandas} \hfill Sep 2023 - Dec 2023}}
{\textit{Data Managment Systems Design Course Project} \hfill \href{https://github.com/vinay-ram1999/CS631-DMSD}{Project Source}}
\begin{zitemize}
\item {Designed and developed a working database for an eComputerStore with all mentioned functionalities.}
\item {Followed a traditional approach for building database by designing an Enhanced Entity Relationship (EER) diagram, transforming the EER model to a Relational database schema and creating the database tables in MySQL using the Relational schema.}
\item {Developed a web application using Streamlit which connects to the MySQL server using a pipeline.}
\end{zitemize}


\subsection{{MURPH Analytics | \textit{Python, Streamlit, Pandas, Matplotlib, Plotly} \hfill Mar 2023 - May 2023}}
{\textit{Personal Project} \hfill \href{https://murph-postprocess.streamlit.app}{Project Source}}
\begin{zitemize}
\item {Built an interactive dashboard using Streamlit to post-process and perform different analytical studies on the simulation data generated from the MURPH Solver.}
\item {Implemented unstructured mesh plotting and 2D contour plots using Plotly.}
% \item {Implementation of 3D plotting and grid independence study }
\end{zitemize}


\subsection{{MURPH | \textit{Python, SymPy, NumPy, OpenMP, CUDA, OP2-API, CFD} \hfill Dec 2022 - Ongoing}}
{\textit{In collaboration with Dr. Satya P. Jammy (Associate Professor, Mechanical Department, SRM University AP)} \hfill \href{https://github.com/UnstructuredFVM}{Project Source}}
\begin{zitemize}
\item {A Multi-dimensional (2-D/3-D), Unstructured-mesh and Reactions based Parallel solver for Hyper-sonic flow regimes.}
\item {New design uproach is used to build the solver code so that the parallel code generation can be fully automated.}
\item {2D Ideal gas solver code is developed and is validated using existing literature.}
\item {Work is underway for integrating species reactions and development of a 3D solver.}
\end{zitemize}


\subsection{{AlgoTrade API | \textit{Python, yfinance, Pandas, Tensorflow, ks-api-client} \hfill May 2022 - Oct 2022}}
{\textit{Personal Project} \hfill \href{https://github.com/vinay-ram1999/AlgoTrade-API}{Project Source}}
\begin{zitemize}
\item {Fully automated NSE Stock/Equity trading-bot for Kotak Securities (KOTAK TRADE API) with integrated back testing and ML algorithms for price and trend predictions.}
\item {The bot gathers any desired stock's historical price data, performs technical analysis using technical indicators and places orders to the stock broker using the broker API.}
\end{zitemize}


%====================
% EXPERIENCE A
%====================
\subsection{{Accelerating a Hypersonic $CO_2$ Reaction Solver | \textit{Python, SymPy, NumPy, OpenMP, CUDA, OP2-API, CFD} \hfill Jul 2020 - May 2021}}
{\textit{B.Tech Final Year Project}}
\begin{zitemize}
\item {A 2-D unstructured ﬁnite volume method based solver capable of simulating hypersonic ﬂows in $CO_2$ rich Martian atmosphere with chemical kinetics for eight species consisting of $N_2 , O_2 , NO, O, N, CO_2 , CO$ and $C$ incorporated in it is developed using pYthon.}
\item {The solver is parallelized to run on single or multiple CPUs and Nvidia GPUs in order to attain greater computational speeds using OP2 application programming interface.}
\end{zitemize}

%====================
% EXPERIENCE B
%====================
%\subsection{{Design and Analysis of Heat Sink \hfill Oct 2020 - Dec 2020}}
%{\textit{Thermal Design of Electronic Equipment Course} \hfill Coursework Project}
%\begin{zitemize}
%\item {Designed and analysed a 2-D heat sink made of Aluminium and a layer of epoxy between the chip and heat sink with specified thermal properties as a thermal design solution for cooling a noval chip (CPU for example) using CFD-HT (Computational Fluid Dynamics and Heat Transfer) software ANSYS Fluent.}
%\end{zitemize}


%====================
% EXPERIENCE C
%====================
% \subsection{{Flow through an Exhaust Manifold \hfill Feb 2020 - May 2020}}
% {\textit{Computational Fluid Dynamics Course} \hfill Coursework Project}
% \begin{zitemize}
% \item {Designed an exhaust manifold for a V-8 engine in Solidworks and then imported this geometry into the Ansys workbench.}
% \item {Using Fluent, simulated the flow of the hot exhaust gases coming out from the engine and designed various diffuser models and studied the flow behavior for different diffuser models and submitted the final report for the optimal design.}
% \end{zitemize}


%====================
% EXPERIENCE D
%====================
% \subsection{{Sub-Sonic Wind tunnel \hfill Sept 2019 - Dec 2019}}
% {\textit{Undergraduate Research Program (UROP)} \hfill Academic Project}
% \begin{zitemize}
% \item {Developed a Subsonic wind tunnel, which is designed to achieve 30m/s in the test section with expected low intensity turbulence level, making it available for researching in areas such as low speed aerodynamics and other such possibilities.}
% \end{zitemize}
